%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\usepackage{multicol}
\usepackage{setspace}

%command for emphasising points/keys among body
\newcommand{\imp}[1] {{\em #1}}

\definecolor{lightgray}{HTML}{000000}

\begin{document}
\header{Joey}{Pereira}
       {co-op student}


\begin{aside}
  \section{contact}
    226 343.9309
    \href{mailto:joey@joeypereira.com}{joey@joeypereira.com}
    ~
    \href{http://joeypereira.com}{joeypereira.com}
    \href{http://www.github.com/xlegoz}{github.com/xlegoz}
  \section{skills}
  avid leader
  adaptable
  %enjoys challenging problems
  %experienced with small teams
  passion for learning
  {\em loves} computer science
  \section{interests}
  	distributed systems
  	reverse engineering
  	operating systems
  	machine learning
  	formal languages
  	compilers and assemblers
  	~
	innovating \& inventing
  	theoretical physics
  	fishing and sailing
  	entrepreneurship
  	new tech
  \section{reverse engineering tools}
  	Java Bytecode Editor
  	Java Decompiler
  	.NET Reflector
  	Ollydbg  	
\end{aside}


\section{about me}
I'm currently a second year undergraduate Computer Science student in the co-op program at the University of Waterloo. I have a passion for theoretical computer science, software development, innovation, and computer security.

%\section{qualifications}
%\begin{multicols}{3}
% avid leader \\ enjoys challenging problems \\ experienced with small teams \\ passion for learning \\ adaptable to any environment \\ {\em loves} computer science
%\end{multicols}

\section{qualifications}
{
  \setlength{\itemsep}{0pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
  \setlength{\itemindent}{0em}
  \setlength{\leftmargin}{0em}
\begin{itemize}
\item Experienced with Java, Racket, C, C++, Bash, Python, Javascript, PHP, and Erlang.
\item Proficient with Git version control, SVN, MySQL databases, and Redis databases.
\item Knowledgeable with network protocols, computer security, and program integrity.
\item Experienced in low level programming, operating systems, and embedded devices.
\item Familiar with Linux, virtual machines, and systems administration.
\item Strong team communication skills and good with customer relations.
\end{itemize}
}

\section{experience}
\begin{entrylist}

  \entry
    {06–08 2013}
    {Framing Carpenter}
    {Katerberg Framing}
    {Involved in small \imp{team collaboration} to achieve \imp{tight deadlines}. \\
    Formulated ways to \imp{optimally complete tasks}   with tools of the trade.
   }

  \entry
  	{2012-2013}
  	{Co-founder and Head Technician}
  	{J\&J Tech}
  	{Investigated starting a \imp{small business} with a partner. \\
	Gained \imp{management skills} through advertising and customer handling. \\
	Underwent management and organizational \imp{responsibilities}.}
	
  \entry
    {06–08 2012}
    {Service Assistant}
    {PlanetCPU}
    {Diagnosed software and hardware problems under \imp{tight time constraints}. \\
    Worked as a \imp{team to complete tasks}, as well as run a market campaign. \\
    Learned how to be a \imp{key contributor} to a small team and to the business.}
\textbf{\emph{Volunteering}} \\
  \entry
  	{2013-2014}
  	{Recruitment Ambassador}
  	{David Cheriton School of Computer Science, uWaterloo}
	{Volunteered in University of Waterloo events for prospective students. \\
  	Set up \imp{technical equipment}  for the events. \\
	Guided prospective students to \imp{discovering computer science} as a passion.}
  \entry
  	{2012-2013}
  	{Technical Organizer}
  	{Elora Road Christian Fellowship}
	{Solved various \imp{technical problems under pressure} to maintain event quality. \\
	\imp{Facilitated} a small worship team and the operation of equipment.}
  	

\end{entrylist}

\section{education}

\begin{entrylist}
  \entry
    {2013-2018}
    {Candidate for Bachelor of Computer Science}
    {University of Waterloo}
	{Projected minor in management studies based on interests of entrepreneurship. \\
	First year representative on Math Endowment Fund Funding Council. \\
	Cumulative average grade of \imp{85\%}. Student of the co-op program.
	\\ %Relevant courses: Designing Functional Programs, Elementary Algorithm Design and Data Abstraction, Logic and Computation, Object-Oriented Software Development, Computer Organization and Design.
 }
 
 \entry
  	{01-02 2014}
  	{Web Development Course}
  	{Udacity (Online)}
  	{Built applications on Google App Engine using Python. }
	
  \entry
  	{07-09 2013}
  	{Startup Engineering Course}
  	{Stanford - Coursera (Online)}
  	{Learned about what it takes to develop an idea from a business perspective. \\
  	Learned node.js while utilizing Platform as a Service.}
  	
  \entry
  	{2009-2013}
  	{Ontario Secondary School Diploma}
  	{Centre Wellington District High School}
    {Led several clubs including a club that taught peers knowledge outside of curriculum and created initiatives to learn with collaboration.}
\end{entrylist}

\newpage 

\begin{asidetwo}  	
	\section{Joey Pereira}
	\section{contact}
    226 343.9309
    \href{mailto:joey@joeypereira.com}{joey@joeypereira.com}
    ~
    \href{http://joeypereira.com}{joeypereira.com}
    \href{http://www.github.com/xlegoz}{github.com/xlegoz}
\end{asidetwo}


\section{projects}

\begin{entrylist}
  \entry
  	{2014}
  	{Pi Net \textsf{- Raspberry Pi Mesh Based Network}}
  	{Still in development}
  	{Intentions to discover the network interaction of multiple devices over a mesh topology network and the sustainability of an intra-net with all nodes.}
  \entry
    {2013-2014}
    {JoOS \textsf{- Bare Bones Operating System \em{- NASM, C}}}
    {\href{http://github.com/xlegoz/JoOS}{github.com/xlegoz/JoOS}}
    {Goal of learning more about the operating system layer and theory. \\
    Involved i386 instruction set, operation at a low level and interrupt handling.}

 
  \entry
  	{2013}
  	{jjNES \textsf{- Nintendo Entertainment System Emulator \em{- Java}}}
  	{Still in research}
  	{Aimed to achieve a better understanding of computer architecture. \\
  	Observed models of how components interact within the NES architecture. \\
  	Built a rudimentary machine code interpreter for 6502 processor.}
  	 
 
  \entry
  	{2013}
  	{Mobile Door Locking \textsf{- Multi-platform door locker \em{- Arduino, Java}}}
  	{Still in invention}
  	{Project to remotely control a deadbolt through mobile devices \\
  	Built using the Arduino platform and with a Java server. \\
  	Utilized various communication streams including email and SMS messages. \\
  	Detailed important security issues such as short-lived authentication.}
\end{entrylist}



\section{achievements}

\begin{entrylist}
  \entry
  	{09 2013}
  	{Google Ship Wars Hackathon \textsf{\em{Top 10}}}
  	{Google, Waterloo}
  	{Developed an AI script which challenged fellow competitors. \\
  	 Acquainted with new tools and an API under a heavy time constraint.}
  \entry
  	{02 2013}
  	{Educational Computing Organization of Ontario Programming Contest \textsf{\em{Semi-finalist}}}
  	{University of Western Ontario}
  	{Directed a team in a highly team-oriented problem solving environment. \\
  	 Utilized critical thinking to translate solutions to code.}
  \entry
	{04 2013}  	
  	{Canadian Computing Contest Certificate of Distinction \textsf{\em{Top 100}}}
  	{University of Waterloo}
  	{Created efficient algorithms to problems by unconventional thinking.}
  \entry
  	{06 2013}
  	{Mathematical Merit Award}
  	{Centre Wellington District High School}
  	{}
  \entry
  	{06 2013}
  	{Ontario Scholar Award}
  	{Centre Wellington District High School}
  	{}

\end{entrylist}

\section{relevant activities}
{\bf reverse engineering: }
{
  \setlength{\itemsep}{0pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
  \setlength{\itemindent}{0em}
  \setlength{\leftmargin}{0em}
\begin{itemize}
\item Driven from a passion to understand the workings of software and what drives a security focus in the development cycle, as well as to discover code structure post-compiling
\item Knowledge of obfuscation and encryption methods for retaining integrity
\item Experience decompiling and analyzing programs, in particular malicious software
\end{itemize}
}

\end{document}
